Predicting Tags for StackOverflow Posts

### 2013-03-17 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 18eb7813e9e7980a50571dd9b0e4e1f95d774dfb [formerly 7e7eefb767de8c0a764f2d01925aaa97b84717f3]
Former-commit-id: 1a908f099316a698171f7e8b7eefa771a0519cc8

\begin{abstract}
  Large-scale behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior, since understanding and modeling hashtag creation can lead to improved human-computer systems that can better identify users' goals and interests.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian probabilistic model that can predict the hashtags used by the author of the post---predicting the users' programming interests.
  The model is 67\% accurate when tasked to predict one tag per post on average.
  This is achieved by choosing the tag that has the highest log odds of being correct,
  given the tag's prior log odds of occurrence and adjusting for the log likelihood ratio of the words in the post being associated with the tag.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.

@@

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{1mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Best-fit coefficient estimates from logistic regression}
    \label{tab:coeffs}
    \vskip 0.12in
    \begin{tabular}{lllll}
      \hline
      Coefficient & 	Estimate &	Std. Err. &	z value &	$Pr(>|z|)$  \\
      \hline
      (Intercept) &	-1.35 &		0.10 &		-13.59 &	\textless2e-16 *** \\
      prior &		1.08 & 		0.01 &		88.12 & 	\textless2e-16 *** \\
      sjiTitle &	1.41 &		0.02 &		57.36 &		\textless2e-16 *** \\
      sjiBody &		2.36 &		0.04 &		58.48 &		\textless2e-16 *** \\
      offset &		-0.71 &		0.02 &		-39.05 &	\textless2e-16 *** \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{3mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Model fit metrics}
    \label{tab:fits}
    \vskip 0.12in
    \begin{tabular}{ll}
      \hline
      Common Name &  Value	\\
      \hline
      McFadden's Pseudo $R_{}^{2}$ &	.46 \\
      True Positives &			647 \\
      False Positives &			278 \\
      True Negatives &			\num{796982} \\
      False Negatives &			\num{2235} \\
      Positive Predictive Value &	0.70 \\
      Negative Predictive Value &	0.997 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

@@

Our StackOverflow model is a successful case showing that ACT-R's declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 67\% of posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.

@@

Our model achieves 67\% classification accuracy when predicting one tag per post on average
(height of full model at vertical dotted line in Figure \ref{fig:ROC})
compared to 47\% accuracy for the co-occurrence model presented in \citeA{Kuo2011}.
Most likely we achieved the increase in model performance by adding some additional model components:
The offset and possibly the body term as well,
as it was unclear if \citeauthor{Kuo2011} used context from both the body and title of a post or just the title.
Also we used two orders of magnitude more posts to train the model co-occurrence matrix ($S_{ji}$).
Nonetheless, there are certainly model similarities:
Co-occurrence count was used as the core measure of similarity, and both local (strength of association) and global (entropy or idf) weighting measures were used to compute tag likelihood, given context.

>>>>

\begin{abstract}
  Large-scale behavioral datasets such as Twitter, Facebook, LinkedIn, StackOverflow, and Yelp can be mined and explored to study human behavior and human computer interaction.
  We focused on hashtag creation as a specific human behavior, since understanding and modeling hashtag creation can lead to improved human-computer systems that can better identify users' goals and interests.
  We explored the StackOverflow dataset, and developed an ACT-R inspired Bayesian probabilistic model that can predict the hashtags used by the author of the post---predicting the users' programming interests.
  The model is 65\% accurate when tasked to predict one tag per post on average.
  This is achieved by choosing the tag that has the highest log odds of being correct,
  given the tag's prior log odds of occurrence and adjusting for the log likelihood ratio of the words in the post being associated with the tag.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.

@@

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{1mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Best-fit coefficient estimates from logistic regression}
    \label{tab:coeffs}
    \vskip 0.12in
    \begin{tabular}{lllll}
      \hline
      Coefficient & 	Estimate &	Std. Err. &	z value &	$Pr(>|z|)$  \\
      \hline
      (Intercept) &	-3.00 &		0.12 &		-25.97 &	\textless2e-16 *** \\
      prior &		0.62 & 		0.01 &		66.94 & 	\textless2e-16 *** \\
      sjiTitle &	0.92 &		0.02 &		39.90 &		\textless2e-16 *** \\
      sjiBody &		1.76 &		0.04 &		43.21 &		\textless2e-16 *** \\
      offset &		0.78 &		0.02 &		33.25 &		\textless2e-16 *** \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{3mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Model fit metrics}
    \label{tab:fits}
    \vskip 0.12in
    \begin{tabular}{ll}
      \hline
      Common Name &  Value	\\
      \hline
      McFadden's Pseudo $R_{}^{2}$ &	.52 \\
      True Positives &			507 \\
      False Positives &			215 \\
      True Negatives &			\num{417409} \\
      False Negatives &			\num{2375} \\
      Positive Predictive Value &	0.70 \\
      Negative Predictive Value &	0.994 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

@@

Our StackOverflow model is a successful case showing that ACT-R's declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 65\% of posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.

@@

Our model achieves 65\% classification accuracy when predicting one tag per post on average
(height of full model at vertical dotted line in Figure \ref{fig:ROC})
compared to 47\% accuracy for the co-occurrence model presented in \citeA{Kuo2011}.
Most likely we achieved the increase in model performance by adding some additional model components:
The offset and possibly the body term as well,
as it was unclear if \citeauthor{Kuo2011} used context from both the body and title of a post or just the title.
Also we used two orders of magnitude more posts to train the model co-occurrence matrix ($S_{ji}$).
Nonetheless, there are certainly model similarities:
Co-occurrence count was used as the core measure of similarity, and both local (strength of association) and global (entropy or idf) weighting measures were used to compute tag likelihood, given context.
